% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}




\begin{document}
%
\begin{titlepage}
    \centering
    \vspace*{1cm}
    
    \Large
    \textbf{Why a Good Boss Likes It When People Complain}
    
    \vspace{1.5cm}
    \normalsize
    Dharmil Vaghasiya\\
    ID: 40230633
    
    \vspace{1cm}
    Concordia University\\
    SOEN - 6841 Software Project Management
    
    \vspace{1.5cm}
    \normalsize
    Professor: Pankaj Kamthan
    
    \vfill
    \today % You can replace '\today' with a specific date if needed
\end{titlepage}



\begin{abstract}
This report explores the multifaceted role of complaints within organizational management, as discussed in Cate Huston's work, "Why a Good Boss Likes It When People Complain." The paper delves into the British cultural context, where complaining is a common practice, not just about mundane matters like weather or tea, but extending to complex issues such as Brexit. Importantly, the paper highlights how complaints, often viewed negatively, are beneficial tools for effective management. 

Complaints are shown to be acts of trust, providing managers with critical insights into underlying problems within their teams. This understanding allows managers to align their strategies and communication more effectively with their team's needs and values. Conflicts within teams, often surfaced through complaints, present opportunities for managers to intervene and facilitate constructive dialogue. Additionally, complaints offer a chance for coaching and clarity, enabling managers to guide team members in expanding their influence and understanding broader organizational contexts.

The report underscores the importance of empathy in management and cautions against the toxicity of excessive complaining, advising the need for boundaries and constructive approaches. In conclusion, the report provides an in-depth analysis of how complaints, when managed effectively, can be instrumental in enhancing trust, transparency, and efficiency within teams.

\keywords{Organizational management \and Complaints \and Employee engagement \and Conflict resolution \and Managerial strategies.}
\vspace{4cm}

\b{Add critical thinking and decision-making. add figures, graphs}


\end{abstract}


\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.

---- Bibliography ----

BibTeX users should specify bibliography style 'splncs04'.
References will then be sorted and formatted in the correct style.

\bibliographystyle{splncs04}
\bibliography{mybibliography}

\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}
